---
output:
  html_document:
    toc: no
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Global Variables, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y))
not_all_na <- function(x) any(!is.na(x))
not_any_na <- function(x) all(!is.na(x))

```


```{r Connect to Data Source, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")

fpax_tbl <- tbl(conn1, "FPAX_MERGED_DETAIL")

fpax_physician_tbl <- tbl(conn1, "PROD_FPAX_PHYSICIAN")
# effort_alloc_tbl <- tbl(conn1, "PROD_EFFORT_ALLOCATION")
cpsc_benchmark_tbl <- tbl(conn1, "DEV_CPSC_BENCHMARK")

access_raw_tbl <- tbl(conn2, "MV_DM_PATIENT_ACCESS")

clarity_ser_tbl <- tbl(conn2, "CLARITY_SER")
clarity_ser_2_tbl <- tbl(conn2, "CLARITY_SER_2")

```


```{r}

report_start_date <- as.Date("1/1/2023", "%m/%d/%Y")
report_end_date <- as.Date("5/1/2025", "%m/%d/%Y")

report_start_period <- as.numeric("202301")
report_end_period <- as.numeric("202504")

report_start_year <- year(report_start_date)
report_end_year <- year(report_end_date)

```


```{r Manual Processing of FPAX Merged Detail Data, echo = FALSE, warning = FALSE, message = FALSE}

### Summarize WRVUs, charges, and collections data by physician and month
### Remove providers under "Unknown DEPT" in CPSC & 0 collections 

fpax_data <- fpax_tbl %>%
  # filter(VOID_FLAG == "N") %>%
  filter(as.numeric(PERIOD) >= report_start_period) %>%
  filter(as.numeric(PERIOD) <= report_end_period) %>%
  filter(is.na(FPSC_DEPARTMENT_DESC) | FPSC_DEPARTMENT_DESC != "UNKNOWN DEPT") %>%
  mutate(YEAR = substr(PERIOD, start = 1 , stop = 4),
         MONTH = substr(PERIOD, start = 5 , stop = 6)) %>%
  group_by(PERIOD, NPI) %>%
  # group_by(PERIOD, PERIOD_QUARTER, YEAR, MONTH,
  #          NPI, MD_NAME, ENTITY_DESC, LOCATION_DESC, EPIC_LOCATION_DESC, EPIC_DEPT_DESC, EPIC_DEPT_ID) %>%
  summarise(WRVU_NUM = sum(WRVU_NUM, na.rm = T),
  # summarise(WRVU_NUM = sum(WRVU_NUM[RVU_COMPUTATION_RULE == "FPSC - Matched Modifiers"], na.rm = T),
            CALC_CHARGE_AMT = sum(CALC_CHARGE_AMT, na.rm = T),
            CALC_PAYMENT_AMT = sum(CALC_PAYMENT_AMT, na.rm = T)) %>%
  group_by(NPI) %>%
  mutate(total_payments = sum(CALC_PAYMENT_AMT, na.rm = T)) %>%
  filter(total_payments > 0) %>%
  dplyr::select(-total_payments) %>%
  collect()



# # Temporary FPAX_Data
# wrvus <- read_excel(file.choose())
# wrvus_clean <- wrvus %>%
#   filter(Month > 2025) %>%
#   mutate(PERIOD = format(as.Date(Month, origin = "1899-12-30"), "%Y%m")) %>%
#   group_by(NPI, PERIOD) %>%
#   summarise(WRVU_NUM = sum(`Work RVUs`, na.rm = T))
# 
# payments <- read_excel(file.choose())
# payments_clean <- payments %>%
#   filter(Month > 2025) %>%
#   mutate(PERIOD = format(as.Date(Month, origin = "1899-12-30"), "%Y%m")) %>%
#   group_by(NPI, PERIOD) %>%
#   summarise(CALC_PAYMENT_AMT = sum(`Total Payments    `, na.rm = T))
# 
# fpax_data <- left_join(wrvus_clean, payments_clean, 
#                        by = c("NPI", "PERIOD"))


```


```{r Global Variables, echo = FALSE, warning = FALSE, message = FALSE}

ytd_YEARMO <- max(fpax_data$PERIOD)
ytd_year <- substr(ytd_YEARMO, start = 1, stop = 4)
ytd_month <- substr(ytd_YEARMO, start = 5, stop = 6)

ytd_month_name <- format(as.Date(paste0(ytd_year,"-",ytd_month,"-01-01")), "%b")

```


```{r Merge Data Tables, echo = FALSE, warning = FALSE, message = FALSE}


effort_alloc <- oracle_updated_merged

### Merge Allocation of Effort and FPAX WRVUs, Charges, and Payments
data_merged_01 <- effort_alloc %>%
  mutate(NPI = as.character(NPI)) %>%
  # dplyr::select(-PROV_ID, PROV_NAME) %>%
  # effort_alloc_tbl %>%
  # collect() %>%
  filter(YEARMO <= ytd_YEARMO) %>% # Filter out months not in fpax data for productivity data processing
  left_join(fpax_data %>%
              mutate(NPI = as.character(NPI)), 
            by = c("NPI" = "NPI",
                   "YEARMO" = "PERIOD"))


### Join PROV_NAME from EPIC Clarity Ser 
data_merged_02 <- data_merged_01 %>%
  left_join(clarity_ser_2_tbl %>%
              dplyr::select(NPI, PROV_ID) %>%
              collect() %>%
              filter(!is.na(NPI)),
            by = c("NPI")) %>%
  left_join(clarity_ser_tbl %>%
              dplyr::select(PROV_ID, PROV_NAME) %>%
              collect() %>%
              rename("NAME" = "PROV_NAME"),
            by = c("PROV_ID")) %>%
  mutate(NAME = ifelse(is.na(NAME), toupper(PHYSICIAN), toupper(NAME)))


### Join CPSC Benchmark 
data_merged_03 <- data_merged_02 %>%
  left_join(cpsc_benchmark_tbl %>%
              collect(), 
            by = c("YEAR" = "YEAR_KEY",
                   "CPSC_SPECIALTY" = "SPECIALTY_DESCRIPTION"))

```


```{r Calculate YTD WRVUs and Payments, echo = FALSE, warning = FALSE, message = FALSE}
 
data_processed <- data_merged_03 %>%
  # rowwise() %>%
  # mutate(ADJ_CFTE = sum(ADJ_CFTE, ADMIN_CLINICAL, na.rm = TRUE)) %>%
  arrange(NAME, LIFE_NUM, NPI, CPSC_SPECIALTY, YEARMO) %>%
  group_by(NAME, LIFE_NUM, NPI, FINANCIAL_SITE, CPSC_SPECIALTY, YEARMO) %>%
  mutate(worked_month_count = row_number()) %>%
  mutate(ann_WRVUs_month = WRVU_NUM*12,
         adj_ann_WRVUs_month = ann_WRVUs_month/ADJ_CFTE,
         payments_per_WRVU_month = CALC_PAYMENT_AMT/WRVU_NUM) %>%
  group_by(NAME, LIFE_NUM, NPI, FINANCIAL_SITE, CPSC_SPECIALTY, YEAR) %>%
  mutate(WRVUs_ytd =  cumsum(replace(WRVU_NUM, is.na(WRVU_NUM), 0)),
         payments_ytd = cumsum(replace(CALC_PAYMENT_AMT, is.na(CALC_PAYMENT_AMT), 0)), 
         CFTE_ytd = round(cumsum(replace(ADJ_CFTE, is.na(ADJ_CFTE), 0))/cumsum(replace(worked_month_count, is.na(worked_month_count), 0)),2),
         worked_month_count_ytd = cumsum(replace(worked_month_count, is.na(worked_month_count), 0))) %>%
  # mutate(WRVUs_ytd = cumsum(WRVU_NUM),
  #        payments_ytd = cumsum(CALC_PAYMENT_AMT),
  #        CFTE_ytd = round(cumsum(ADJ_CFTE)/cumsum(worked_month_count),2),
  #        worked_month_count_ytd = cumsum(worked_month_count)) %>%
  ungroup() %>%
  mutate(ann_WRVUs_ytd = WRVUs_ytd/worked_month_count_ytd*12,
         adj_ann_WRVUs_ytd = ann_WRVUs_ytd/CFTE_ytd,
         payments_per_WRVU_ytd = payments_ytd/WRVUs_ytd) %>%
  arrange(MASTER_DEPT, NPI, YEAR, MONTH)


```


```{r Calculate Productivity Percentile, echo = FALSE, warning = FALSE, message = FALSE}

# Match adjusted annualized month & ytd WRVUs to benchmarks --------------------
percentile_match <- data_processed[, c("adj_ann_WRVUs_month", "adj_ann_WRVUs_ytd", paste0("P", seq(1,100)))]

percentile_match_month <- as.data.frame(apply(percentile_match %>% dplyr::select(-adj_ann_WRVUs_ytd), 1, function(x) min(tail(x,100)[tail(x,100)>=head(x,1)])))
colnames(percentile_match_month) <- c("percentile_match_month")

percentile_match_ytd <- as.data.frame(apply(percentile_match %>% dplyr::select(-adj_ann_WRVUs_month), 1, function(x) min(tail(x,100)[tail(x,100)>=head(x,1)])))
colnames(percentile_match_ytd) <- c("percentile_match_ytd")

percentile_match <- bind_cols(percentile_match, percentile_match_month)
percentile_match <- bind_cols(percentile_match, percentile_match_ytd)

percentile_match <- percentile_match %>%
  rowwise() %>%
  mutate(productivity_month = ifelse(is.infinite(percentile_match_month), "P100", 
                                     ifelse(is.nan(percentile_match_month), NA,
                                            ifelse(adj_ann_WRVUs_month > P100, "P100", 
                                                   names(.)[which(c_across(P1:P100) == percentile_match_month)+1])))) %>%
  mutate(productivity_ytd = ifelse(is.infinite(percentile_match_ytd), "P100", 
                                     ifelse(is.nan(percentile_match_ytd), NA,
                                            ifelse(adj_ann_WRVUs_ytd > P100, "P100", 
                                                   names(.)[which(c_across(P1:P100) == percentile_match_ytd)+1])))) %>%
  mutate(productivity_month = ifelse(productivity_month == "adj_ann_WRVUs_ytd", "P0", productivity_month),
         productivity_ytd = ifelse(productivity_ytd == "adj_ann_WRVUs_ytd", "P0", productivity_ytd))


percentile_match <- percentile_match %>%
  mutate(productivity_month = as.numeric(gsub("P","",productivity_month))/100,
         productivity_ytd = as.numeric(gsub("P","",productivity_ytd))/100)


# Master CPSC Data with Productivity Calculations ------------------------------
productivity_data <- bind_cols(data_processed, percentile_match[,c("productivity_month", "productivity_ytd")])


# Remove productivities with no CFTE 
productivity_data <- productivity_data %>%
  mutate(productivity_month = ifelse(is.na(ADJ_CFTE) | CFTE_ytd <= 0, NA, productivity_month),
         productivity_ytd = ifelse(is.na(CFTE_ytd) | CFTE_ytd <= 0, NA, productivity_ytd))
  

```


```{r Filter Roster for Productivity, echo = FALSE, warning = FALSE, message = FALSE}

### Physicians with NPIs in Roster
productivity_data_filtered <- productivity_data %>%
  filter(!is.na(NPI)) %>%
  group_by(NPI) %>%
  mutate(total_payments = sum(CALC_PAYMENT_AMT, na.rm = T)) %>%
  filter(total_payments > 0) %>%
  dplyr::select(-LIFE_NUM)


### Calculate Effort % 
productivity_data_filtered <- productivity_data_filtered %>%
  rowwise() %>%
  mutate(C_EFFORT = round(sum(CLINICAL, CLINICAL_RESIDENT, SERVICE, SERVICE_RESIDENT, NON_BILLABLE_OFFSITE_CLINICAL, na.rm = T)/FTE,2),
         A_EFFORT = round(sum(ADMIN_DEP_HOSP, ADMIN_RESIDENCY, ADMIN_CLINICAL, na.rm = T)/FTE,2),
         R_EFFORT = round(sum(RESEARCH_FUNDED, RESEARCH_UNFUNDED, RESEARCH_INTRAMURAL_FUNDED, na.rm = T)/FTE,2),
         T_EFFORT = round(TEACHING/FTE,2),
         TOTAL_EFFORT = sum(C_EFFORT, A_EFFORT,  R_EFFORT, T_EFFORT, na.rm = T))
  

# admin_title <- productivity_data_filtered %>% group_by(NPI, ADMIN_TITLE) %>% summarise(total = n()) %>% filter(!is.na(ADMIN_TITLE))
# productivity_data_filtered$ADMIN_TITLE <- admin_title$ADMIN_TITLE[match(productivity_data_filtered$NPI, admin_title$NPI)]
# 
# term_date <- productivity_data_filtered %>% group_by(NPI, TERM_DATE) %>% summarise(total = n()) %>% filter(!is.na(TERM_DATE))
# productivity_data_filtered$TERM_DATE <- term_date$TERM_DATE[match(productivity_data_filtered$NPI, term_date$NPI)]

```


```{r Calculate Variance to Target, echo = FALSE, warning = FALSE, message = FALSE}

# Calculate wrvu variance and realization from benchmark
productivity_data_filtered <-  productivity_data_filtered %>%
  mutate(`Var to P25 Target (CFTE Adj)` = ifelse(adj_ann_WRVUs_ytd < P25, (P25-adj_ann_WRVUs_ytd)*ADJ_CFTE, NA),
         `Var to P50 Target (CFTE Adj)` = ifelse(adj_ann_WRVUs_ytd < P50, (P50-adj_ann_WRVUs_ytd)*ADJ_CFTE, NA),
         `Var to P75 Target (CFTE Adj)` = ifelse(adj_ann_WRVUs_ytd < P75, (P75-adj_ann_WRVUs_ytd)*ADJ_CFTE, NA),
         `Var to P90 Target (CFTE Adj)` = ifelse(adj_ann_WRVUs_ytd < P90, (P90-adj_ann_WRVUs_ytd)*ADJ_CFTE, NA),
         `P25 Target Realized` = ifelse(adj_ann_WRVUs_ytd < P25, (adj_ann_WRVUs_ytd/P25), NA),
         `P50 Target Realized` = ifelse(adj_ann_WRVUs_ytd < P50, (adj_ann_WRVUs_ytd/P50), NA),
         `P75 Target Realized` = ifelse(adj_ann_WRVUs_ytd < P75, (adj_ann_WRVUs_ytd/P75), NA),
         `P90 Target Realized` = ifelse(adj_ann_WRVUs_ytd < P90, (adj_ann_WRVUs_ytd/P90), NA))

```



```{r Process Data Output for Monthly Export, echo = FALSE, warning = FALSE, message = FALSE}

# productivity_data <- productivity_data %>% filter(NPI %!in% c("1780614891", "1073117164"))

# Column Name Setup
month_col_names <- unique(format(sort(as.Date(paste0(paste0(unique(paste0(productivity_data_filtered$YEAR,"-",productivity_data_filtered$MONTH)),"-01")))), "%b %y"))
year_col_names <- sort(unique(productivity_data_filtered$YEAR))


# Calculate % Total Effort by Year 
yearly_effort_output <- productivity_data_filtered %>%
  rename(`P25 wRVU Target` = P25,
         `P50 wRVU Target` = P50,
         `P75 wRVU Target` = P75,
         `P90 wRVU Target` = P90) %>%
  group_by(MASTER_DEPT, FINANCIAL_SITE, CPSC_SPECIALTY, NAME, NPI, ADMIN_TITLE, TYPE, TYPE_DETAIL, HIRE_DATE, TERM_DATE, FTE, YEAR,
           `P25 wRVU Target`, `P50 wRVU Target`, `P75 wRVU Target`, `P90 wRVU Target`) %>%
  summarise(`Clinical Effort` = round(mean(C_EFFORT, na.rm = T),2),
            `Admin Effort` = round(mean(A_EFFORT, na.rm = T),2),
            `Research Effort` = round(mean(R_EFFORT, na.rm = T),2),
            `Teaching Effort` = round(mean(T_EFFORT, na.rm = T),2),
            `Total Effort (=100%)` = round(mean(TOTAL_EFFORT, na.rm = T),2)) %>%
  pivot_wider(names_from = YEAR,
              values_from = c(FTE, `Clinical Effort`, `Admin Effort`, `Research Effort`, `Teaching Effort`, `Total Effort (=100%)`, `P25 wRVU Target`, `P50 wRVU Target`, `P75 wRVU Target`, `P90 wRVU Target`),
              names_glue = "{.value} {YEAR}") %>%
  # mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  # mutate_if(is.numeric, list(~na_if(., Inf))) %>% 
  # mutate_if(is.numeric, list(~na_if(., -Inf)))%>%
  distinct() %>%
  group_by(NPI, NAME) %>% 
  mutate(duplicates = n()) 


duplicates <- yearly_effort_output %>% filter(duplicates > 1)


effort_cols <- c("Clinical Effort", "Admin Effort", "Research Effort", "Teaching Effort", "Total Effort (=100%)")
percentile_cols <- c("P25 wRVU Target", "P50 wRVU Target", "P75 wRVU Target", "P90 wRVU Target")
yearly_effort_cols <- c("MASTER_DEPT", "FINANCIAL_SITE", "CPSC_SPECIALTY", "NAME", "NPI", "ADMIN_TITLE", "TYPE", "TYPE_DETAIL", "HIRE_DATE", "TERM_DATE", 
                        paste0("FTE ", rep(year_col_names, each = 1)),
                        paste0(effort_cols, " ", rep(year_col_names, each = 5)),
                        paste0(percentile_cols, " ", rep(year_col_names, each = 4)))

yearly_effort_output <- yearly_effort_output[yearly_effort_cols]



monthly_productivity_output <- productivity_data_filtered %>%
  dplyr::select(MASTER_DEPT, FINANCIAL_SITE, CPSC_SPECIALTY, NAME, NPI, ADMIN_TITLE, TYPE, TYPE_DETAIL, HIRE_DATE, TERM_DATE, 
                ADJ_CFTE, YEARMO,
                WRVU_NUM, CALC_PAYMENT_AMT, 
                productivity_month) %>%
  pivot_wider(names_from = YEARMO,
              values_from = c(ADJ_CFTE, WRVU_NUM, CALC_PAYMENT_AMT, productivity_month))

# check <- monthly_productivity_output %>%
#   group_by(MASTER_DEPT, CPSC_SPECIALTY, PROV_NAME, NPI, ADMIN_TITLE, PROV_TYPE, LATEST_HIRE_DATE, TERM_DATE, YEARMO) %>%
#   summarise(total = n())
# 
# which(duplicated(monthly_productivity_output))

ytd_productivity_output <- productivity_data_filtered %>%
  filter(MONTH == ytd_month) %>%
  arrange(YEARMO) %>%
  dplyr::select(MASTER_DEPT, FINANCIAL_SITE, CPSC_SPECIALTY, NPI, YEARMO,
                CFTE_ytd, 
                WRVUs_ytd, ann_WRVUs_ytd, adj_ann_WRVUs_ytd,  
                payments_ytd, payments_per_WRVU_ytd, productivity_ytd) %>%
  pivot_wider(names_from = YEARMO,
              values_from = c(CFTE_ytd, 
                              WRVUs_ytd, ann_WRVUs_ytd, adj_ann_WRVUs_ytd,  
                              payments_ytd, payments_per_WRVU_ytd,
                              productivity_ytd))
  # tidyr::unnest()

yearly_productivity_output <- productivity_data_filtered %>%
  group_by(MASTER_DEPT, FINANCIAL_SITE, CPSC_SPECIALTY, NAME, NPI, ADMIN_TITLE, TYPE, TYPE_DETAIL, HIRE_DATE, TERM_DATE, YEAR) %>%
  slice(which.max(YEARMO)) %>%
  arrange(YEARMO) %>%
  dplyr::select(MASTER_DEPT, FINANCIAL_SITE, CPSC_SPECIALTY, NPI, YEAR, 
                CFTE_ytd, 
                WRVUs_ytd, ann_WRVUs_ytd, adj_ann_WRVUs_ytd,  
                payments_ytd, payments_per_WRVU_ytd, productivity_ytd) %>%
  pivot_wider(names_from = YEAR,
              values_from = c( CFTE_ytd, 
                               WRVUs_ytd, ann_WRVUs_ytd, adj_ann_WRVUs_ytd,  
                               payments_ytd, payments_per_WRVU_ytd,
                               productivity_ytd))

colnames(yearly_productivity_output) = gsub("_ytd", "", colnames(yearly_productivity_output))



yearly_target_var_output <- productivity_data_filtered %>%
  group_by(MASTER_DEPT, FINANCIAL_SITE, CPSC_SPECIALTY, NAME, NPI, ADMIN_TITLE, TYPE, TYPE_DETAIL, HIRE_DATE, TERM_DATE, YEAR) %>%
  slice(which.max(YEARMO)) %>%
  arrange(YEARMO) %>%
  dplyr::select(MASTER_DEPT, FINANCIAL_SITE, CPSC_SPECIALTY, NAME, NPI, ADMIN_TITLE, TYPE, TYPE_DETAIL, HIRE_DATE, TERM_DATE,
                `Var to P25 Target (CFTE Adj)`, `Var to P50 Target (CFTE Adj)`, `Var to P75 Target (CFTE Adj)`, `Var to P90 Target (CFTE Adj)`,
                `P25 Target Realized`, `P50 Target Realized`, `P75 Target Realized`, `P90 Target Realized`) %>%
  pivot_wider(names_from = YEAR,
              values_from = c(`Var to P25 Target (CFTE Adj)`, `Var to P50 Target (CFTE Adj)`, `Var to P75 Target (CFTE Adj)`, `Var to P90 Target (CFTE Adj)`,
                              `P25 Target Realized`, `P50 Target Realized`, `P75 Target Realized`, `P90 Target Realized`),
              names_glue = "{.value} {YEAR}")
  

target_var_cols <- c("Var to P25 Target (CFTE Adj)", "Var to P50 Target (CFTE Adj)", "Var to P75 Target (CFTE Adj)", "Var to P90 Target (CFTE Adj)")
target_realized_cols <- c("P25 Target Realized", "P50 Target Realized", "P75 Target Realized", "P90 Target Realized")
yearly_target_var_cols <- c("MASTER_DEPT", "CPSC_SPECIALTY", "NAME", "NPI", "ADMIN_TITLE", "TYPE", "TYPE_DETAIL", "HIRE_DATE", "TERM_DATE", 
                            paste0(target_var_cols, " ", rep(year_col_names, each = 4)),
                            paste0(target_realized_cols, " ", rep(year_col_names, each = 4)))


yearly_target_var_output <- yearly_target_var_output[yearly_target_var_cols]


# Merge Sub-tables 
productivity_output_merged <- left_join(yearly_effort_output, monthly_productivity_output)
productivity_output_merged <- left_join(productivity_output_merged, ytd_productivity_output)
productivity_output_merged <- left_join(productivity_output_merged, yearly_productivity_output)
productivity_output_merged <- left_join(productivity_output_merged, yearly_target_var_output)

```


```{r Format Monthly Export, echo = FALSE, warning = FALSE, message = FALSE}

colnames(productivity_output_merged)  <-  c("Master Dept", "Site", "CPSC Specialty", "Physician", "NPI", "Admin Title", 
                                          "Physician Type", "Type Detail",  "Hire Date", "Term Date", 
                                          yearly_effort_cols[11:length(yearly_effort_cols)],
                                          paste0("CFTE ", month_col_names),
                                          paste0("WRVUs ", month_col_names), 
                                          paste0("Collections ", month_col_names),
                                          paste0("Productivity ", month_col_names),
                                          paste0("CFTE YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                          paste0("WRVUs YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                          paste0("WRVUs YTD Annualized ", "Jan-", ytd_month_name, " ", year_col_names),
                                          paste0("WRVUs YTD Annualized FTE ", "Jan-", ytd_month_name, " ", year_col_names),
                                          paste0("Collections YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                          paste0("$ per WRVU YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                          paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                          paste0("CFTE ", year_col_names),
                                          paste0("WRVUs ", year_col_names),
                                          paste0("WRVUs Annualized ", year_col_names),
                                          paste0("WRVUs Annualized FTE ", year_col_names),
                                          paste0("Collections ", year_col_names),
                                          paste0("$ per WRVU ", year_col_names),
                                          paste0("Productivity ", year_col_names),
                                          yearly_target_var_cols[10:length(yearly_target_var_cols)])


# Sort Final Output 
productivity_output_merged <- productivity_output_merged %>%
  arrange(`Master Dept`, `CPSC Specialty`, `Physician`)

# write_csv(productivity_output_merged, "productivity_output_merged_review.csv")

```


```{r Format Excel Export Data, echo = FALSE, warning = FALSE, message = FALSE}


## Format columns as numeric for number formatting in Excel
productivity_output_export <- productivity_output_merged %>%
  ungroup() %>%
  mutate_all(as.character) %>%
  replace(.=="NULL", NA) %>%
  replace(.=="NA", NA) %>%
  # mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  mutate(across(contains("FTE") | contains("Collections") | contains("CFTE") | contains("Effort") | contains("Target") 
                | contains("WRVU") | contains("Productivity"), ~as.numeric(.))) 
  # mutate(across(contains('FTE|Collections|WRVUs')) ~as.numeric(.)) %>%
  # mutate_if(is.numeric, list(~na_if(., Inf))) %>%
  # mutate_if(is.numeric, list(~na_if(., -Inf)))
  # mutate(across(starts_with('wRVU | WRVUs | Collections'), round, 0))
  # mutate(across(contains('NPI | Effort | wRVU | CFTE | WRVUs | Collections'), ~as.character(.))) %>%
  # mutate(across(contains('NPI | Effort | wRVU | CFTE | WRVUs | Collections'), ~as.numeric(.))) 


productivity_output_export[sapply(productivity_output_export, is.infinite)] <- NA
productivity_output_export[sapply(productivity_output_export, is.nan)] <- NA
# write.xlsx(productivity_output_export, "productivity_output_export.xlsx")


sort_col <- grep(paste("Productivity", ytd_year , sep=" "), colnames(productivity_output_export))

productivity_output_export <- productivity_output_export %>%
  # arrange(desc(`Productivity 2024`))
  arrange(desc(.[[sort_col]]), `Master Dept`)

## Productivity Data Filtered for Physicians 
productivity_output_export_physicians <- productivity_output_export %>% 
  filter(`Physician Type` == "Physician") %>%
  filter(is.na(`Type Detail`)) 
```



```{r Filter Data to Relevant Departmentes, echo = FALSE, warning = FALSE, message = FALSE}


list_master_dept <- c(
                      # "Anesthesiology",
                      "Breast Surgery",
                      "Cancer",
                      "Cardiology",
                      "Cardiovascular Surgery",
                      # "Critical Care",
                      # "Dentistry",
                      "Dermatology",
                      # "Emergency Medicine",
                      # "Environmental Medicine and Climate Science",
                      # "Family Medicine & Community Health",
                      # "Genetics",
                      "Geriatrics",
                      # "Global Health",
                      # "ICCM",
                      # "Medical Education",
                      "Medicine",
                      # "MSB",
                      "MSDMG",
                      # "MSQ",
                      # "MSSN",
                      "Network",
                      # "Neurology",
                      "Neurosurgery",
                      "OBGYN",
                      "Ophthalmology",
                      "Orthopaedics",
                      "Otolaryngology",
                      # "Pathology",
                      "Pediatrics",
                      # "Pharmacological Sciences",
                      # "Population Health Science and Policy",
                      # "Psychiatry",
                      # "Public Health",
                      # "Radiation Oncology",
                      # "Radiology",
                      "Rehab Medicine",
                      "Surgery",
                      "Thoracic Surgery",
                      "Transplant",
                      "Urology"
                      )


```



```{r Format Excel Export File, echo = FALSE, warning = FALSE, message = FALSE}

library(openxlsx)

## Data Section
### Formatting Style 
provStyle <- createStyle(fgFill = "#dddedd", textDecoration = "bold", wrapText = TRUE)
prior_effortStyle <- createStyle(fgFill = "#4F81BD", fontColour  = "#FFFFFF", textDecoration = "bold", wrapText = TRUE)
current_effortStyle <- createStyle(fgFill = "#4BACC6", fontColour  = "#FFFFFF", textDecoration = "bold", wrapText = TRUE)
prior_percentileStyle <- createStyle(fgFill = "#92D050", textDecoration = "bold", wrapText = TRUE)
current_percentileStyle <- createStyle(fgFill = "#FFC000", textDecoration = "bold", wrapText = TRUE)

wRVUsStyle <- createStyle(fgFill = "#00aeef", fontColour  = "#FFFFFF", textDecoration = "bold", wrapText = TRUE)
collectionsStyle <- createStyle(fgFill = "#d80b8c", fontColour  = "#FFFFFF", textDecoration = "bold", wrapText = TRUE)
cfteStyle <- createStyle(fgFill = "#7030a0", fontColour  = "#FFFFFF", textDecoration = "bold", wrapText = TRUE)
productivityStyle <- createStyle(fgFill = "#212070", fontColour  = "#FFFFFF", textDecoration = "bold", wrapText = TRUE)
# varianceStyle <- createStyle(fgFill = "#ffc000", fontColour  = "#000000", textDecoration = "bold", wrapText = TRUE)
perwRVUStyle <- createStyle(fgFill = "#a5a7a5", fontColour  = "#FFFFFF", textDecoration = "bold", wrapText = TRUE)

varTargetStyle <- createStyle(fgFill = "#E97132", textDecoration = "bold", wrapText = TRUE)
realizedTargetStyle <- createStyle(fgFill = "#92D050", textDecoration = "bold", wrapText = TRUE)

number_format = createStyle(numFmt="#,##0", fontColour  = "#000000")
decimal_format = createStyle(numFmt="0.00", fontColour  = "#000000")
dollar_format = createStyle(numFmt="$#,##0", fontColour  = "#000000")
percent_format = createStyle(numFmt="#,##0%", fontColour  = "#000000")
# percent_format = createStyle(numFmt="#,##0%", fgFill = "#ECECFA", textDecoration = "bold", borderStyle = "thin", borderColour = "black")

redStyle <- createStyle(bgFill = "#FFC7CE", fontColour = "#9C0006", textDecoration = "bold", border = "TopBottomLeftRight", borderColour = "#D9D9D9")
orangeStyle <- createStyle(bgFill = "#FFEB9C",fontColour = "#9C5700", textDecoration = "bold", border = "TopBottomLeftRight", borderColour = "#D9D9D9")
greenStyle <- createStyle(bgFill = "#C6EFCE", fontColour = "#006100", textDecoration = "bold", border = "TopBottomLeftRight", borderColour = "#D9D9D9")


## Group Columns for Formatting
prov_detail_col_group <- c(1:10)

FTE_col_group <- which(colnames(productivity_output_export) %in% paste0("FTE ", year_col_names))

prior_effort_col_group <- which(colnames(productivity_output_export) %in% 
                                  paste0(rep(c("Clinical Effort ", "Admin Effort ", "Research Effort ", "Teaching Effort ", "Total Effort (=100%) "), length(year_col_names)-1),
                                         rep(head(year_col_names, -1), each = 5)))

cur_effort_col_group <- which(colnames(productivity_output_export) %in% 
                                  paste0(c("Clinical Effort ", "Admin Effort ", "Research Effort ", "Teaching Effort ", "Total Effort (=100%) "), tail(year_col_names, 1)))

prior_perc_col_group <- which(colnames(productivity_output_export) %in% 
                                  paste0(rep(c("P25 wRVU Target ", "P50 wRVU Target ", "P75 wRVU Target ", "P90 wRVU Target "), length(year_col_names)-1),
                                         rep(head(year_col_names, -1), each = 5)))
cur_perc_col_group <- which(colnames(productivity_output_export) %in% 
                                  paste0(c("P25 wRVU Target ", "P50 wRVU Target ", "P75 wRVU Target ", "P90 wRVU Target "), tail(year_col_names, 1)))


monthly_cfte_col_group <-  grep("CFTE ", colnames(productivity_output_export))
monthly_wrvu_col_group <- grep("WRVUs ", colnames(productivity_output_export))
monthly_collections_col_group <- grep("Collections ", colnames(productivity_output_export))
monthly_productivity_col_group <- which(colnames(productivity_output_export) %in% paste0("Productivity ", month_col_names))


# ytd_cfte_col_group <- which(colnames(productivity_output_export) %in% paste0("CFTE YTD ", month_col_names))
# ytd_wrvu_col_group <- which(colnames(productivity_output_export) %in%  paste0("WRVUs YTD ", "Jan-", ytd_month_name, " ", year_col_names))
# ytd_wrvu_ann_col_group <- which(colnames(productivity_output_export) %in%  paste0("WRVUs YTD Annualized ", "Jan-", ytd_month_name, " ", year_col_names))
ytd_wrvu_ann_adj_col_group <- which(colnames(productivity_output_export) %in%  paste0("WRVUs YTD Annualized FTE ", "Jan-", ytd_month_name, " ", year_col_names))
# ytd_collections_col_group <- grep("Collections YTD", colnames(productivity_output_export))

ytd_dollar_wrvu_col_group <- which(colnames(productivity_output_export) %in% paste0("$ per WRVU YTD ", "Jan-", ytd_month_name, " ", year_col_names))
ytd_productivity_col_group <- which(colnames(productivity_output_export) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names))

year_dollar_wrvu_col_group <- which(colnames(productivity_output_export) %in% paste0("$ per WRVU ", year_col_names))
year_productivity_col_group <-  which(colnames(productivity_output_export) %in% paste0("Productivity ", year_col_names))

year_target_var_col_group <- grep("Var to P", colnames(productivity_output_export))
year_target_realized_col_group <- grep("Realized", colnames(productivity_output_export))


```


```{r Create Excel Export Master, echo = FALSE, warning = FALSE, message = FALSE}

library(openxlsx)

  ## Productivity Snapshot -----------------------------------------------------
  ## create a workbook and add a worksheet
  wb <- createWorkbook()
  addWorksheet(wb, paste0("Master Prod (", month_col_names[length(month_col_names)], ")"))
  
  
  ## Title Section
  wb_title <- paste0("Master Productivity Summary ", month_col_names[1], " - ",  month_col_names[length(month_col_names)])
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 1, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 1, titleStyle, rows = 1, cols = 1)
  
  ## Subtitle Section
  wb_subtitle <- paste0("*Includes providers with collections >$0 since ", month_col_names[1])
  subtitleStyle <- createStyle(fontSize = 14,
                            textDecoration = c("italic"), 
                            valign = "center")
  
  writeData(wb, 1, wb_subtitle, startRow = 2, startCol = 1)
  addStyle(wb, 1, subtitleStyle, rows = 2, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 10
  
  
  ### Data Output 
  master_prod_summary <- productivity_output_export %>% 
                             filter(is.na(`Term Date`) | as.Date(`Term Date`, "%m/%d/%Y") >= report_start_date) %>%
                             filter(`Master Dept` %in% list_master_dept) %>%
                             ungroup() %>%
                             filter(!is.na(`Master Dept`)) %>%
                             arrange(`Master Dept`) %>%
                             dplyr::select(prov_detail_col_group, 
                                           paste0("CFTE YTD ", "Jan-", ytd_month_name, " ", year_col_names), 
                                           paste0("WRVUs YTD Annualized ", "Jan-", ytd_month_name, " ", year_col_names), 
                                           paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                           paste("CFTE", year_col_names), 
                                           paste("WRVUs Annualized", year_col_names), 
                                           paste("Productivity", year_col_names))
  
  writeDataTable(wb, 1, master_prod_summary,
                 startRow = 3, startCol = 1, tableStyle = "None")
  
  addStyle(wb, 1, provStyle, rows = row_start, cols = prov_detail_col_group)
  
  #### YTD Data Section
  addStyle(wb, 1, cfteStyle,
           rows = row_start,
           cols = grep("CFTE", colnames(master_prod_summary)))
  addStyle(wb, 1, decimal_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("CFTE", colnames(master_prod_summary)), gridExpand = TRUE)
  
  
  addStyle(wb, 1, wRVUsStyle,
           rows = row_start,
           cols = grep("WRVUs", colnames(master_prod_summary)))
  addStyle(wb, 1, number_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("WRVUs", colnames(master_prod_summary)), gridExpand = TRUE)
  
  
  addStyle(wb, 1, productivityStyle,
           rows = row_start,
           cols = grep("Productivity", colnames(master_prod_summary)))
  addStyle(wb, 1, percent_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("Productivity", colnames(master_prod_summary)), gridExpand = TRUE)
  
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols =  which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols =  which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  
  freezePane(wb, 1, firstActiveRow = row_start+1, firstActiveCol = 5)
  
  
  # set zoom
  set_zoom <- function(x) gsub('(?<=zoomScale=")[0-9]+', x, sV, perl = TRUE)
  
  sV <- wb$worksheets[[1]]$sheetViews
  wb$worksheets[[1]]$sheetViews <- set_zoom(90)
  
  
  


  ## Master Productivity Detail Tab --------------------------------------------
  addWorksheet(wb, paste0("Master Prod Detail (", month_col_names[length(month_col_names)], ")"))
  
  ## Title Section
  wb_title <- paste0("Master Productivity Detail ", month_col_names[1], " - ",  month_col_names[length(month_col_names)])
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 2, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 2, titleStyle, rows = 1, cols = 1)
  
  ## Subtitle Section
  wb_subtitle <- paste0("*Includes providers with collections >$0 since ", month_col_names[1])
  subtitleStyle <- createStyle(fontSize = 14,
                            textDecoration = c("italic"), 
                            valign = "center")
  
  writeData(wb, 2, wb_subtitle, startRow = 2, startCol = 1)
  addStyle(wb, 2, subtitleStyle, rows = 2, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 10
  
  
  ### Data Output 
  writeDataTable(wb, 2,
                 productivity_output_export %>% 
                   filter(is.na(`Term Date`) | as.Date(`Term Date`, "%m/%d/%Y") >= report_start_date) %>%
                   filter(`Master Dept` %in% list_master_dept) %>%
                   ungroup() %>%
                   filter(!is.na(`Master Dept`)) %>%
                   arrange(`Master Dept`), 
                 startRow = 3, startCol = 1, tableStyle = "None")
  
  addStyle(wb, 2, provStyle, rows = row_start, cols = prov_detail_col_group)
  
  addStyle(wb, 2, provStyle, rows = row_start, cols = FTE_col_group)
  
#### % Effort Section ----------------------------------------------------------
  #### % Effort by Prior Year
  addStyle(wb, 2, prior_effortStyle, 
           rows = row_start, 
           cols = prior_effort_col_group)
  addStyle(wb, 2, percent_format, 
           rows = (row_start+1):(row_start+nrow(productivity_output_export)), 
           cols = prior_effort_col_group, gridExpand = TRUE)
  
  groupColumns(wb, 2, cols = prior_effort_col_group, hidden = TRUE)
  
  #### % Effort by Current Year
  addStyle(wb, 2, current_effortStyle, 
           rows = row_start, 
           cols = cur_effort_col_group)
  addStyle(wb, 2, percent_format, 
           rows = (row_start+1):(row_start+nrow(productivity_output_export)), 
           cols = cur_effort_col_group, gridExpand = TRUE)
   
  
  #### Percentile Target Section -------------------------------------------------
  #### Percentile by Prior Year
  addStyle(wb, 2, prior_percentileStyle,
           rows = row_start,
           cols = prior_perc_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = prior_perc_col_group, gridExpand = TRUE)
  
  
  
  #### Percentile by Current Year
  addStyle(wb, 2, current_percentileStyle,
           rows = row_start,
           cols = cur_perc_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = cur_perc_col_group, gridExpand = TRUE)
  
  groupColumns(wb, 2, cols = c(prior_perc_col_group, cur_perc_col_group), hidden = TRUE)
  
  
  #### Monthly Data Section ------------------------------------------------------
  #### CFTE by Month
  addStyle(wb, 2, cfteStyle,
           rows = row_start,
           cols = monthly_cfte_col_group)
  addStyle(wb, 2, decimal_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = monthly_cfte_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols =  monthly_cfte_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_cfte_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  which(colnames(productivity_output_export) %in% paste0("CFTE ", month_col_names)), hidden = TRUE)
  
  
  #### WRVUs by Month
  addStyle(wb, 2, wRVUsStyle,
           rows = row_start,
           cols = monthly_wrvu_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = monthly_wrvu_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = monthly_wrvu_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_wrvu_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  which(colnames(productivity_output_export) %in% paste0("WRVUs ", month_col_names)), hidden = TRUE)
  
  
  #### Collections by Month
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = monthly_collections_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = monthly_collections_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = monthly_collections_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_collections_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols = which(colnames(productivity_output_export) %in% paste0("Collections ", month_col_names)), hidden = TRUE)
  
  
  #### Productivity by Month
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = monthly_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols =  monthly_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  setColWidths(wb, 2, cols = monthly_productivity_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_productivity_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  monthly_productivity_col_group, hidden = TRUE)
  
  
  
  
  #### Comments for WRVUs
  c1 <- createComment(comment = "Total YTD WRVUs generated, annualized, and adjusted to YTD CFTE", 
                      style = createStyle(fontSize = 12),
                      visible = FALSE)
  writeComment(wb, 2,
               row = row_start,
               col = tail(ytd_wrvu_ann_adj_col_group, 1),
               comment = c1)
  
  # addStyle(wb, 2, cfteStyle,
  #          rows = row_start,
  #          cols = ytd_cfte_col_group)
  # addStyle(wb, 2, decimal_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export)),
  #          cols = ytd_cfte_col_group, gridExpand = TRUE)
  # 
  # 
  # addStyle(wb, 2, wRVUsStyle,
  #          rows = row_start,
  #          cols = ytd_wrvu_col_group)
  # addStyle(wb, 2, number_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export)),
  #          cols = ytd_wrvu_col_group, gridExpand = TRUE)
  # 
  # addStyle(wb, 2, collectionsStyle,
  #          rows = row_start,
  #          cols = ytd_collections_col_group)
  # addStyle(wb, 2, dollar_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export)),
  #          cols = ytd_collections_col_group, gridExpand = TRUE)
  # 
  # 
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = ytd_dollar_wrvu_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = ytd_dollar_wrvu_col_group, gridExpand = TRUE)
  
  
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = ytd_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = ytd_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols = ytd_productivity_col_group,
                        rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols = ytd_productivity_col_group,
                        rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols = ytd_productivity_col_group,
                        rule = ">=.75", style = greenStyle)
  
  
  
  #### Year Data Section
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = year_dollar_wrvu_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = year_dollar_wrvu_col_group, gridExpand = TRUE)
  
  
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = year_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = year_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols = year_productivity_col_group,
                        rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols = year_productivity_col_group,
                        rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export)),
                        cols = year_productivity_col_group,
                        rule = ">=.75", style = greenStyle)
  
  
  
  #### Variance to Target Section
  addStyle(wb, 2, varTargetStyle,
           rows = row_start,
           cols = year_target_var_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = year_target_var_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = year_target_var_col_group, widths = 12)
  # groupColumns(wb, 1, cols = head(year_target_var_col_group, (length(year_col_names)-1)*4), hidden = TRUE)
  groupColumns(wb, 2, cols = head(year_target_var_col_group, (length(year_col_names))*4), hidden = TRUE)
  
  
  
  #### Target Realized Section
  addStyle(wb, 2, realizedTargetStyle,
           rows = row_start,
           cols = year_target_realized_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export)),
           cols = year_target_realized_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = year_target_realized_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(year_target_realized_col_group, (length(year_col_names)-1)*4), hidden = TRUE)
  groupColumns(wb, 2, cols =  head(year_target_realized_col_group, (length(year_col_names))*4), hidden = TRUE)
  
  #### Table Formatting 
  # setColWidths(wb, 1, cols = c(1,2,3,5), widths = 25)
  # setColWidths(wb, 1, cols = c(4), widths = 15)
  # 
  # setColWidths(wb, 1, cols = (col_start+month_col_num*4):length(productivity_output_export), widths = 15)
  # # groupColumns(wb, 1, cols = c((col_start+month_col_num*1):(col_start+(month_col_num*4)-1)), hidden = TRUE)
  
  freezePane(wb, 2, firstActiveRow = row_start+1, firstActiveCol = 5)
  
  
  # addWorksheet(wb, paste0(year_col_names[length(year_col_names)], " Benchmarks"))
  # writeDataTable(wb, 2, benchmark_data %>% filter(`Year Key` == year_col_names[length(year_col_names)]), startRow = 1, startCol = 1, tableStyle = "None")
  
  
  # set zoom
  set_zoom <- function(x) gsub('(?<=zoomScale=")[0-9]+', x, sV, perl = TRUE)
  
  sV <- wb$worksheets[[2]]$sheetViews
  wb$worksheets[[2]]$sheetViews <- set_zoom(90)
  
  
  
  # Definitions Tab --------------------------------------------------------------
  addWorksheet(wb, "Definitions")
  
  ## Title Section
  wb_title <- "Allocation of Effort (CARTS) Definitions"
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 3, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 3, titleStyle, rows = 1, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 9
  
  
  ### Definitions Table 
  definitions <- data.frame(
  Category = c("Clinical", "Clinical With Resident", "Service", "Service With Resident",	"Non-Billable Offsite Clinical Time",
               "Department/ Hospital Admin",	"Residency Program Admin",	"Clinical Admin",	
               "Research",
               # "Research Funded",	"Research Unfunded", "Research Intramurally Funded",
               "School Teaching"),
  Definition   = c("Activities related to billable physician patient care. Any clinical services rendered and billed through the Faculty Practice.",
                   "Activities related to billable patient care with a resident present.",
                   "Clinical services rendered in Hospital locations for time spent in non-billable direct patient care activities such as Medicaid clinic visits where the professional fees are NOT billed or paid very poorly for services provided.",
                   "Clinical services rendered in Hospital locations for time spent in non-billable direct patient care activities such as Medicaid clinic visits where the professional fees are NOT billed or paid very poorly for services provided.",
                   "Activities related to non-billable physician patient care. None of the billing or RVUs roll back to Mount Sinai.",
                   "Work-effort related to administration of departmental services and programs; school-related administrative services. Work-effort related to administration of hospital related services. Administrative time associated with hospital services (critical care, stroke, etc.) should be defined as Hospital Administrative effort.",
                   "Any administrative time (with or without an official title) spent supporting the residency program. Administrative time associated with hospital clinic is considered Residency Program Administration time.",
                   "Clinical non-patient facing activities such as patient charting and patient communications.",
                   "Time spent executing grant related activities, including effort devoted to; extramurally sponsored research projects; research and/or clinical trial effort which is paid for by an institution budget or philanthropy account; to a sponsored research training program; effort devoted to sponsored clinical trials.",
                   "Preparation and instruction time related to teaching medical student courses and residency program effort (e.g., Grand Rounds). Time spent with residents performing clinical duties should be classified under clinical or service as appropriate."),
  Example = c("Time spent in the FPA without a resident present.",
              "Time spent in the FPA with a resident present.",
              "Ryan, IMA, inpatient clinics without a resident present.",
              "Ryan, IMA, inpatient clinics with a resident present.",
              "Time spent at EHC/QHC, Bronx VA, etc.",
              "Committee service, FPA quality roles, FPA Medical Director, IRB service, and other departmental services. Hospital-based Quality roles, Medical Directors of labs, clinics, operating rooms, inpatient units, or other hospital-based settings; Medical/Quality Directors (infection control).",
              "Residency Program Director, Fellowship Program Director (if accredited fellowship program), time spent on Grand Rounds presentations, interviews, resident evaluations, etc. should be included in this time.",
              "Time spent on charting, EPIC In-Basket Communications, etc.",
              "Sponsored/not sponsored research training, clinical trials, grant-funded activities.",
              " ")
)
  
  ### Data Output 
  writeDataTable(wb, 3, definitions, startRow = 3, startCol = 1, tableStyle = "TableStyleLight9")
  
  addStyle(wb, 3, createStyle(wrapText = TRUE),
           rows = (row_start):(row_start+nrow(definitions)),
           cols = c(1,2,3), gridExpand = TRUE)
  
  setColWidths(wb, 3, cols = c(1), widths = 35)
  setColWidths(wb, 3, cols = c(2), widths = 60)
  setColWidths(wb, 3, cols = c(3), widths = 40)
  
  
  # CPSC BENCHMARK Tab --------------------------------------------------------------
  addWorksheet(wb, "CPSC Benchmark")
  
  ## Title Section
  wb_title <- "CPSC Benchmark"
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 4, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 4, titleStyle, rows = 1, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 9
  
  
  ### CPSC Benchmark
  cpsc_benchmark <- cpsc_benchmark_tbl %>% 
    collect() %>%
    filter(YEAR_KEY >= 2023) %>%
    arrange(YEAR_KEY, SPECIALTY_DESCRIPTION_ORG)
    
  
  ### Data Output 
  writeDataTable(wb, 4, cpsc_benchmark, startRow = 3, startCol = 1, tableStyle = "TableStyleLight9")
  
  addStyle(wb, 4, number_format,
         rows = (row_start+1):(row_start+nrow(cpsc_benchmark)),
         cols = 5:length(cpsc_benchmark), gridExpand = TRUE)


### Export Excel Report
saveWorkbook(wb, paste0("~/monthly-productivity-file-email/master-files/Master Productivity Data_",  month_col_names[length(month_col_names)],".xlsx"), overwrite = T)

# saveWorkbook(wb, "/nfs/data/Applications/Ambulatory/master_productivity_data.xlsx", overwrite = T)

# openXL(wb)

```


```{r Create Excel Export Physicians, echo = FALSE, warning = FALSE, message = FALSE}

library(openxlsx)

## Productivity Snapshot -----------------------------------------------------
  ## create a workbook and add a worksheet
  wb <- createWorkbook()
  addWorksheet(wb, paste0("Master Prod (", month_col_names[length(month_col_names)], ")"))
  
  
  ## Title Section
  wb_title <- paste0("Master Physician Productivity Summary ", month_col_names[1], " - ",  month_col_names[length(month_col_names)])
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 1, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 1, titleStyle, rows = 1, cols = 1)
  
  ## Subtitle Section
  wb_subtitle <- paste0("*Includes providers with collections >$0 since ", month_col_names[1])
  subtitleStyle <- createStyle(fontSize = 14,
                            textDecoration = c("italic"), 
                            valign = "center")
  
  writeData(wb, 1, wb_subtitle, startRow = 2, startCol = 1)
  addStyle(wb, 1, subtitleStyle, rows = 2, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 10
  
  
  ### Data Output 
  master_prod_summary <- productivity_output_export_physicians %>% 
                             filter(is.na(`Term Date`) | as.Date(`Term Date`, "%m/%d/%Y") >= report_start_date) %>%
                             filter(`Master Dept` %in% list_master_dept) %>%
                             ungroup() %>%
                             filter(!is.na(`Master Dept`)) %>%
                             arrange(`Master Dept`) %>%
                             dplyr::select(prov_detail_col_group, 
                                           paste0("CFTE YTD ", "Jan-", ytd_month_name, " ", year_col_names), 
                                           paste0("WRVUs YTD Annualized ", "Jan-", ytd_month_name, " ", year_col_names), 
                                           paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                           paste("CFTE", year_col_names), 
                                           paste("WRVUs Annualized", year_col_names), 
                                           paste("Productivity", year_col_names))
  
  writeDataTable(wb, 1, master_prod_summary,
                 startRow = 3, startCol = 1, tableStyle = "None")
  
  addStyle(wb, 1, provStyle, rows = row_start, cols = prov_detail_col_group)
  
  #### YTD Data Section
  addStyle(wb, 1, cfteStyle,
           rows = row_start,
           cols = grep("CFTE", colnames(master_prod_summary)))
  addStyle(wb, 1, decimal_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("CFTE", colnames(master_prod_summary)), gridExpand = TRUE)
  
  
  addStyle(wb, 1, wRVUsStyle,
           rows = row_start,
           cols = grep("WRVUs", colnames(master_prod_summary)))
  addStyle(wb, 1, number_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("WRVUs", colnames(master_prod_summary)), gridExpand = TRUE)
  
  
  addStyle(wb, 1, productivityStyle,
           rows = row_start,
           cols = grep("Productivity", colnames(master_prod_summary)))
  addStyle(wb, 1, percent_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("Productivity", colnames(master_prod_summary)), gridExpand = TRUE)
  
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols =  which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols =  which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  
  freezePane(wb, 1, firstActiveRow = row_start+1, firstActiveCol = 5)
  
  
  # set zoom
  set_zoom <- function(x) gsub('(?<=zoomScale=")[0-9]+', x, sV, perl = TRUE)
  
  sV <- wb$worksheets[[1]]$sheetViews
  wb$worksheets[[1]]$sheetViews <- set_zoom(90)
  
  
  


  ## Master Productivity Detail Tab --------------------------------------------
  addWorksheet(wb, paste0("Master Prod Detail (", month_col_names[length(month_col_names)], ")"))
  
  ## Title Section
  wb_title <- paste0("Master Physician Productivity Detail ", month_col_names[1], " - ",  month_col_names[length(month_col_names)])
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 2, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 2, titleStyle, rows = 1, cols = 1)
  
  ## Subtitle Section
  wb_subtitle <- paste0("*Includes providers with collections >$0 since ", month_col_names[1])
  subtitleStyle <- createStyle(fontSize = 14,
                            textDecoration = c("italic"), 
                            valign = "center")
  
  writeData(wb, 2, wb_subtitle, startRow = 2, startCol = 1)
  addStyle(wb, 2, subtitleStyle, rows = 2, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 10
  
  
  ### Data Output 
  writeDataTable(wb, 2,
                 productivity_output_export_physicians %>% 
                   filter(is.na(`Term Date`) | as.Date(`Term Date`, "%m/%d/%Y") >= report_start_date) %>%
                   filter(`Master Dept` %in% list_master_dept) %>%
                   ungroup() %>%
                   filter(!is.na(`Master Dept`)) %>%
                   arrange(`Master Dept`), 
                 startRow = 3, startCol = 1, tableStyle = "None")
  
  addStyle(wb, 2, provStyle, rows = row_start, cols = prov_detail_col_group)
  
  addStyle(wb, 2, provStyle, rows = row_start, cols = FTE_col_group)
  
#### % Effort Section ----------------------------------------------------------
  #### % Effort by Prior Year
  addStyle(wb, 2, prior_effortStyle, 
           rows = row_start, 
           cols = prior_effort_col_group)
  addStyle(wb, 2, percent_format, 
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)), 
           cols = prior_effort_col_group, gridExpand = TRUE)
  
  groupColumns(wb, 2, cols = prior_effort_col_group, hidden = TRUE)
  
  #### % Effort by Current Year
  addStyle(wb, 2, current_effortStyle, 
           rows = row_start, 
           cols = cur_effort_col_group)
  addStyle(wb, 2, percent_format, 
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)), 
           cols = cur_effort_col_group, gridExpand = TRUE)
   
  
  
  #### Percentile Target Section -------------------------------------------------
  #### Percentile by Prior Year
  addStyle(wb, 2, prior_percentileStyle,
           rows = row_start,
           cols = prior_perc_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = prior_perc_col_group, gridExpand = TRUE)
  
  
  groupColumns(wb, 2, cols = prior_perc_col_group, hidden = TRUE)
  
  
  #### Percentile by Current Year
  addStyle(wb, 2, current_percentileStyle,
           rows = row_start,
           cols = cur_perc_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = cur_perc_col_group, gridExpand = TRUE)
  
  
  #### Monthly Data Section ------------------------------------------------------
  #### CFTE by Month
  addStyle(wb, 2, cfteStyle,
           rows = row_start,
           cols = monthly_cfte_col_group)
  addStyle(wb, 2, decimal_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = monthly_cfte_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols =  monthly_cfte_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_cfte_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  which(colnames(productivity_output_export_physicians) %in% paste0("CFTE ", month_col_names)), hidden = TRUE)
  
  
  #### WRVUs by Month
  addStyle(wb, 2, wRVUsStyle,
           rows = row_start,
           cols = monthly_wrvu_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = monthly_wrvu_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = monthly_wrvu_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_wrvu_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  which(colnames(productivity_output_export_physicians) %in% paste0("WRVUs ", month_col_names)), hidden = TRUE)
  
  
  #### Collections by Month
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = monthly_collections_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = monthly_collections_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = monthly_collections_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_collections_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols = which(colnames(productivity_output_export_physicians) %in% paste0("Collections ", month_col_names)), hidden = TRUE)
  
  
  #### Productivity by Month
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = monthly_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols =  monthly_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  setColWidths(wb, 2, cols = monthly_productivity_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_productivity_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  monthly_productivity_col_group, hidden = TRUE)
  
  
  
  
  #### YTD Data Section
  # addStyle(wb, 2, cfteStyle,
  #          rows = row_start,
  #          cols = ytd_cfte_col_group)
  # addStyle(wb, 2, decimal_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
  #          cols = ytd_cfte_col_group, gridExpand = TRUE)
  # 
  # 
  # addStyle(wb, 2, wRVUsStyle,
  #          rows = row_start,
  #          cols = ytd_wrvu_col_group)
  # addStyle(wb, 2, number_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
  #          cols = ytd_wrvu_col_group, gridExpand = TRUE)
  # 
  # addStyle(wb, 2, collectionsStyle,
  #          rows = row_start,
  #          cols = ytd_collections_col_group)
  # addStyle(wb, 2, dollar_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
  #          cols = ytd_collections_col_group, gridExpand = TRUE)
  # 
  # 
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = ytd_dollar_wrvu_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = ytd_dollar_wrvu_col_group, gridExpand = TRUE)
  
  
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = ytd_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = ytd_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols = ytd_productivity_col_group,
                        rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols = ytd_productivity_col_group,
                        rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols = ytd_productivity_col_group,
                        rule = ">=.75", style = greenStyle)
  
  
  
  #### Year Data Section
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = year_dollar_wrvu_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = year_dollar_wrvu_col_group, gridExpand = TRUE)
  
  
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = year_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = year_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols = year_productivity_col_group,
                        rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols = year_productivity_col_group,
                        rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
                        cols = year_productivity_col_group,
                        rule = ">=.75", style = greenStyle)
  
  
  
  #### Variance to Target Section
  addStyle(wb, 2, varTargetStyle,
           rows = row_start,
           cols = year_target_var_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = year_target_var_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = year_target_var_col_group, widths = 12)
  # groupColumns(wb, 1, cols = head(year_target_var_col_group, (length(year_col_names)-1)*4), hidden = TRUE)
  groupColumns(wb, 2, cols = head(year_target_var_col_group, (length(year_col_names))*4), hidden = TRUE)
  
  
  
  #### Target Realized Section
  addStyle(wb, 2, realizedTargetStyle,
           rows = row_start,
           cols = year_target_realized_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians)),
           cols = year_target_realized_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = year_target_realized_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(year_target_realized_col_group, (length(year_col_names)-1)*4), hidden = TRUE)
  groupColumns(wb, 2, cols =  head(year_target_realized_col_group, (length(year_col_names))*4), hidden = TRUE)
  
  #### Table Formatting 
  # setColWidths(wb, 1, cols = c(1,2,3,5), widths = 25)
  # setColWidths(wb, 1, cols = c(4), widths = 15)
  # 
  # setColWidths(wb, 1, cols = (col_start+month_col_num*4):length(productivity_output_export_physicians), widths = 15)
  # # groupColumns(wb, 1, cols = c((col_start+month_col_num*1):(col_start+(month_col_num*4)-1)), hidden = TRUE)
  
  freezePane(wb, 2, firstActiveRow = row_start+1, firstActiveCol = 5)
  
  
  # addWorksheet(wb, paste0(year_col_names[length(year_col_names)], " Benchmarks"))
  # writeDataTable(wb, 2, benchmark_data %>% filter(`Year Key` == year_col_names[length(year_col_names)]), startRow = 1, startCol = 1, tableStyle = "None")
  
  
  # set zoom
  set_zoom <- function(x) gsub('(?<=zoomScale=")[0-9]+', x, sV, perl = TRUE)
  
  sV <- wb$worksheets[[2]]$sheetViews
  wb$worksheets[[2]]$sheetViews <- set_zoom(90)
  
  
  
  # Definitions Tab --------------------------------------------------------------
  addWorksheet(wb, "Definitions")
  
  ## Title Section
  wb_title <- "Allocation of Effort (CARTS) Definitions"
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 3, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 3, titleStyle, rows = 1, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 9
  
  
  ### Definitions Table 
  definitions <- data.frame(
  Category = c("Clinical", "Clinical With Resident", "Service", "Service With Resident",	"Non-Billable Offsite Clinical Time",
               "Department/ Hospital Admin",	"Residency Program Admin",	"Clinical Admin",	
               "Research",
               # "Research Funded",	"Research Unfunded", "Research Intramurally Funded",
               "School Teaching"),
  Definition   = c("Activities related to billable physician patient care. Any clinical services rendered and billed through the Faculty Practice.",
                   "Activities related to billable patient care with a resident present.",
                   "Clinical services rendered in Hospital locations for time spent in non-billable direct patient care activities such as Medicaid clinic visits where the professional fees are NOT billed or paid very poorly for services provided.",
                   "Clinical services rendered in Hospital locations for time spent in non-billable direct patient care activities such as Medicaid clinic visits where the professional fees are NOT billed or paid very poorly for services provided.",
                   "Activities related to non-billable physician patient care. None of the billing or RVUs roll back to Mount Sinai.",
                   "Work-effort related to administration of departmental services and programs; school-related administrative services. Work-effort related to administration of hospital related services. Administrative time associated with hospital services (critical care, stroke, etc.) should be defined as Hospital Administrative effort.",
                   "Any administrative time (with or without an official title) spent supporting the residency program. Administrative time associated with hospital clinic is considered Residency Program Administration time.",
                   "Clinical non-patient facing activities such as patient charting and patient communications.",
                   "Time spent executing grant related activities, including effort devoted to; extramurally sponsored research projects; research and/or clinical trial effort which is paid for by an institution budget or philanthropy account; to a sponsored research training program; effort devoted to sponsored clinical trials.",
                   "Preparation and instruction time related to teaching medical student courses and residency program effort (e.g., Grand Rounds). Time spent with residents performing clinical duties should be classified under clinical or service as appropriate."),
  Example = c("Time spent in the FPA without a resident present.",
              "Time spent in the FPA with a resident present.",
              "Ryan, IMA, inpatient clinics without a resident present.",
              "Ryan, IMA, inpatient clinics with a resident present.",
              "Time spent at EHC/QHC, Bronx VA, etc.",
              "Committee service, FPA quality roles, FPA Medical Director, IRB service, and other departmental services. Hospital-based Quality roles, Medical Directors of labs, clinics, operating rooms, inpatient units, or other hospital-based settings; Medical/Quality Directors (infection control).",
              "Residency Program Director, Fellowship Program Director (if accredited fellowship program), time spent on Grand Rounds presentations, interviews, resident evaluations, etc. should be included in this time.",
              "Time spent on charting, EPIC In-Basket Communications, etc.",
              "Sponsored/not sponsored research training, clinical trials, grant-funded activities.",
              " ")
)
  
  ### Data Output 
  writeDataTable(wb, 3, definitions, startRow = 3, startCol = 1, tableStyle = "TableStyleLight9")
  
  addStyle(wb, 3, createStyle(wrapText = TRUE),
           rows = (row_start):(row_start+nrow(definitions)),
           cols = c(1,2,3), gridExpand = TRUE)
  
  setColWidths(wb, 3, cols = c(1), widths = 35)
  setColWidths(wb, 3, cols = c(2), widths = 60)
  setColWidths(wb, 3, cols = c(3), widths = 40)
  
  
  # CPSC BENCHMARK Tab --------------------------------------------------------------
  addWorksheet(wb, "CPSC Benchmark")
  
  ## Title Section
  wb_title <- "CPSC Benchmark"
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 4, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 4, titleStyle, rows = 1, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 9
  
  
  ### CPSC Benchmark
  cpsc_benchmark <- cpsc_benchmark_tbl %>% 
    collect() %>%
    filter(YEAR_KEY >= 2023) %>%
    arrange(YEAR_KEY, SPECIALTY_DESCRIPTION_ORG)
    
  
  ### Data Output 
  writeDataTable(wb, 4, cpsc_benchmark, startRow = 3, startCol = 1, tableStyle = "TableStyleLight9")
  
  addStyle(wb, 4, number_format,
         rows = (row_start+1):(row_start+nrow(cpsc_benchmark)),
         cols = 5:length(cpsc_benchmark), gridExpand = TRUE)

# Export Excel Report
saveWorkbook(wb, paste0("~/monthly-productivity-file-email/master-files/Master Physician Productivity Data_",  month_col_names[length(month_col_names)],".xlsx"), overwrite = T)
# saveWorkbook(wb, "/nfs/data/Applications/Ambulatory/master_productivity_data.xlsx", overwrite = T)

# openXL(wb)

```


```{r Department Excel Export Physicians Function, echo = FALSE, warning = FALSE, message = FALSE}

library(openxlsx)


list_master_dept <- as.vector(sort(unique(productivity_output_export_physicians$`Master Dept`)))

# 
# department_filter <- "Dermatology"

productivity_file_function <- function(department_filter){

  
    ## Format columns as numeric for number formatting in Excel
  productivity_output_export_physicians_filtered <- productivity_output_export_physicians %>%
    filter(is.na(`Term Date`) | as.Date(`Term Date`, "%m/%d/%Y") >= report_start_date) %>%
                   arrange(`Master Dept`) %>%
    filter(`Master Dept` == department_filter) %>%
     mutate(across(contains('CFTE|WRVUs|Collections'), ~as.numeric(.)))
  
  
    wb <- createWorkbook()
  addWorksheet(wb, paste0("Master Prod (", month_col_names[length(month_col_names)], ")"))
  
  
  ## Title Section
  wb_title <- paste0("Master Physician Productivity Summary ", month_col_names[1], " - ",  month_col_names[length(month_col_names)])
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 1, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 1, titleStyle, rows = 1, cols = 1)
  
  ## Subtitle Section
  wb_subtitle <- paste0("*Includes providers with collections >$0 since ", month_col_names[1])
  subtitleStyle <- createStyle(fontSize = 14,
                            textDecoration = c("italic"), 
                            valign = "center")
  
  writeData(wb, 1, wb_subtitle, startRow = 2, startCol = 1)
  addStyle(wb, 1, subtitleStyle, rows = 2, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 10
  
  
  ### Data Output 
  master_prod_summary <- productivity_output_export_physicians_filtered %>% 
                             filter(is.na(`Term Date`) | as.Date(`Term Date`, "%m/%d/%Y") >= report_start_date) %>%
                             filter(`Master Dept` %in% list_master_dept) %>%
                             ungroup() %>%
                             filter(!is.na(`Master Dept`)) %>%
                             arrange(`Master Dept`) %>%
                             dplyr::select(prov_detail_col_group, 
                                           paste0("CFTE YTD ", "Jan-", ytd_month_name, " ", year_col_names), 
                                           paste0("WRVUs YTD Annualized ", "Jan-", ytd_month_name, " ", year_col_names), 
                                           paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names),
                                           paste("CFTE", year_col_names), 
                                           paste("WRVUs Annualized", year_col_names), 
                                           paste("Productivity", year_col_names))
  
  writeDataTable(wb, 1, master_prod_summary,
                 startRow = 3, startCol = 1, tableStyle = "None")
  
  addStyle(wb, 1, provStyle, rows = row_start, cols = prov_detail_col_group)
  
  #### YTD Data Section
  addStyle(wb, 1, cfteStyle,
           rows = row_start,
           cols = grep("CFTE", colnames(master_prod_summary)))
  addStyle(wb, 1, decimal_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("CFTE", colnames(master_prod_summary)), gridExpand = TRUE)
  
  
  addStyle(wb, 1, wRVUsStyle,
           rows = row_start,
           cols = grep("WRVUs", colnames(master_prod_summary)))
  addStyle(wb, 1, number_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("WRVUs", colnames(master_prod_summary)), gridExpand = TRUE)
  
  
  addStyle(wb, 1, productivityStyle,
           rows = row_start,
           cols = grep("Productivity", colnames(master_prod_summary)))
  addStyle(wb, 1, percent_format,
           rows = (row_start+1):(row_start+nrow(master_prod_summary)),
           cols = grep("Productivity", colnames(master_prod_summary)), gridExpand = TRUE)
  
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste0("Productivity YTD ", "Jan-", ytd_month_name, " ", year_col_names)),
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols = which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols =  which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 1,
                        rows = (row_start+1):(row_start+nrow(master_prod_summary)),
                        cols =  which(colnames(master_prod_summary) %in% paste("Productivity", year_col_names)),
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  
  freezePane(wb, 1, firstActiveRow = row_start+1, firstActiveCol = 5)
  
  
  # set zoom
  set_zoom <- function(x) gsub('(?<=zoomScale=")[0-9]+', x, sV, perl = TRUE)
  
  sV <- wb$worksheets[[1]]$sheetViews
  wb$worksheets[[1]]$sheetViews <- set_zoom(90)
  
  
  


  ## Master Productivity Detail Tab --------------------------------------------
  addWorksheet(wb, paste0("Master Prod Detail (", month_col_names[length(month_col_names)], ")"))
  
  ## Title Section
  wb_title <- paste0("Master Physician Productivity Detail ", month_col_names[1], " - ",  month_col_names[length(month_col_names)])
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 2, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 2, titleStyle, rows = 1, cols = 1)
  
  ## Subtitle Section
  wb_subtitle <- paste0("*Includes providers with collections >$0 since ", month_col_names[1])
  subtitleStyle <- createStyle(fontSize = 14,
                            textDecoration = c("italic"), 
                            valign = "center")
  
  writeData(wb, 2, wb_subtitle, startRow = 2, startCol = 1)
  addStyle(wb, 2, subtitleStyle, rows = 2, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 10
  
  
  ### Data Output 
  writeDataTable(wb, 2,
                 productivity_output_export_physicians_filtered %>% 
                   filter(is.na(`Term Date`) | as.Date(`Term Date`, "%m/%d/%Y") >= report_start_date) %>%
                   filter(`Master Dept` %in% list_master_dept) %>%
                   ungroup() %>%
                   filter(!is.na(`Master Dept`)) %>%
                   arrange(`Master Dept`), 
                 startRow = 3, startCol = 1, tableStyle = "None")
  
  addStyle(wb, 2, provStyle, rows = row_start, cols = prov_detail_col_group)
  
  addStyle(wb, 2, provStyle, rows = row_start, cols = FTE_col_group)
  
#### % Effort Section ----------------------------------------------------------
  #### % Effort by Prior Year
  addStyle(wb, 2, prior_effortStyle, 
           rows = row_start, 
           cols = prior_effort_col_group)
  addStyle(wb, 2, percent_format, 
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)), 
           cols = prior_effort_col_group, gridExpand = TRUE)
  
  groupColumns(wb, 2, cols = prior_effort_col_group, hidden = TRUE)
  
  #### % Effort by Current Year
  addStyle(wb, 2, current_effortStyle, 
           rows = row_start, 
           cols = cur_effort_col_group)
  addStyle(wb, 2, percent_format, 
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)), 
           cols = cur_effort_col_group, gridExpand = TRUE)
   
  
  
  #### Percentile Target Section -------------------------------------------------
  #### Percentile by Prior Year
  addStyle(wb, 2, prior_percentileStyle,
           rows = row_start,
           cols = prior_perc_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = prior_perc_col_group, gridExpand = TRUE)
  
  
  groupColumns(wb, 2, cols = prior_perc_col_group, hidden = TRUE)
  
  
  #### Percentile by Current Year
  addStyle(wb, 2, current_percentileStyle,
           rows = row_start,
           cols = cur_perc_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = cur_perc_col_group, gridExpand = TRUE)
  
  
  #### Monthly Data Section ------------------------------------------------------
  #### CFTE by Month
  addStyle(wb, 2, cfteStyle,
           rows = row_start,
           cols = monthly_cfte_col_group)
  addStyle(wb, 2, decimal_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = monthly_cfte_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols =  monthly_cfte_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_cfte_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  which(colnames(productivity_output_export_physicians_filtered) %in% paste0("CFTE ", month_col_names)), hidden = TRUE)
  
  
  #### WRVUs by Month
  addStyle(wb, 2, wRVUsStyle,
           rows = row_start,
           cols = monthly_wrvu_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = monthly_wrvu_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = monthly_wrvu_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_wrvu_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  which(colnames(productivity_output_export_physicians_filtered) %in% paste0("WRVUs ", month_col_names)), hidden = TRUE)
  
  
  #### Collections by Month
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = monthly_collections_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = monthly_collections_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = monthly_collections_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_collections_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols = which(colnames(productivity_output_export_physicians_filtered) %in% paste0("Collections ", month_col_names)), hidden = TRUE)
  
  
  #### Productivity by Month
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = monthly_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols =  monthly_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols =  monthly_productivity_col_group,
                        type = "expression", rule = ">=.75", style = greenStyle)
  
  setColWidths(wb, 2, cols = monthly_productivity_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(monthly_productivity_col_group, (length(year_col_names)-1)*12), hidden = TRUE)
  groupColumns(wb, 2, cols =  monthly_productivity_col_group, hidden = TRUE)
  
  
  
  
  #### YTD Data Section
  # addStyle(wb, 2, cfteStyle,
  #          rows = row_start,
  #          cols = ytd_cfte_col_group)
  # addStyle(wb, 2, decimal_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
  #          cols = ytd_cfte_col_group, gridExpand = TRUE)
  # 
  # 
  # addStyle(wb, 2, wRVUsStyle,
  #          rows = row_start,
  #          cols = ytd_wrvu_col_group)
  # addStyle(wb, 2, number_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
  #          cols = ytd_wrvu_col_group, gridExpand = TRUE)
  # 
  # addStyle(wb, 2, collectionsStyle,
  #          rows = row_start,
  #          cols = ytd_collections_col_group)
  # addStyle(wb, 2, dollar_format,
  #          rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
  #          cols = ytd_collections_col_group, gridExpand = TRUE)
  # 
  # 
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = ytd_dollar_wrvu_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = ytd_dollar_wrvu_col_group, gridExpand = TRUE)
  
  
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = ytd_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = ytd_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols = ytd_productivity_col_group,
                        rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols = ytd_productivity_col_group,
                        rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols = ytd_productivity_col_group,
                        rule = ">=.75", style = greenStyle)
  
  
  
  #### Year Data Section
  addStyle(wb, 2, collectionsStyle,
           rows = row_start,
           cols = year_dollar_wrvu_col_group)
  addStyle(wb, 2, dollar_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = year_dollar_wrvu_col_group, gridExpand = TRUE)
  
  
  addStyle(wb, 2, productivityStyle,
           rows = row_start,
           cols = year_productivity_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = year_productivity_col_group, gridExpand = TRUE)
  
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols = year_productivity_col_group,
                        rule = "<.50", style = redStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols = year_productivity_col_group,
                        rule = ">=.50", style = orangeStyle)
  conditionalFormatting(wb, 2,
                        rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
                        cols = year_productivity_col_group,
                        rule = ">=.75", style = greenStyle)
  
  
  
  #### Variance to Target Section
  addStyle(wb, 2, varTargetStyle,
           rows = row_start,
           cols = year_target_var_col_group)
  addStyle(wb, 2, number_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = year_target_var_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = year_target_var_col_group, widths = 12)
  # groupColumns(wb, 1, cols = head(year_target_var_col_group, (length(year_col_names)-1)*4), hidden = TRUE)
  groupColumns(wb, 2, cols = head(year_target_var_col_group, (length(year_col_names))*4), hidden = TRUE)
  
  
  
  #### Target Realized Section
  addStyle(wb, 2, realizedTargetStyle,
           rows = row_start,
           cols = year_target_realized_col_group)
  addStyle(wb, 2, percent_format,
           rows = (row_start+1):(row_start+nrow(productivity_output_export_physicians_filtered)),
           cols = year_target_realized_col_group, gridExpand = TRUE)
  
  setColWidths(wb, 2, cols = year_target_realized_col_group, widths = 12)
  # groupColumns(wb, 1, cols =  head(year_target_realized_col_group, (length(year_col_names)-1)*4), hidden = TRUE)
  groupColumns(wb, 2, cols =  head(year_target_realized_col_group, (length(year_col_names))*4), hidden = TRUE)
  
  #### Table Formatting 
  # setColWidths(wb, 1, cols = c(1,2,3,5), widths = 25)
  # setColWidths(wb, 1, cols = c(4), widths = 15)
  # 
  # setColWidths(wb, 1, cols = (col_start+month_col_num*4):length(productivity_output_export_physicians_filtered), widths = 15)
  # # groupColumns(wb, 1, cols = c((col_start+month_col_num*1):(col_start+(month_col_num*4)-1)), hidden = TRUE)
  
  freezePane(wb, 2, firstActiveRow = row_start+1, firstActiveCol = 5)
  
  
  # addWorksheet(wb, paste0(year_col_names[length(year_col_names)], " Benchmarks"))
  # writeDataTable(wb, 2, benchmark_data %>% filter(`Year Key` == year_col_names[length(year_col_names)]), startRow = 1, startCol = 1, tableStyle = "None")
  
  
  # set zoom
  set_zoom <- function(x) gsub('(?<=zoomScale=")[0-9]+', x, sV, perl = TRUE)
  
  sV <- wb$worksheets[[2]]$sheetViews
  wb$worksheets[[2]]$sheetViews <- set_zoom(90)
  
  
  
  # Definitions Tab --------------------------------------------------------------
  addWorksheet(wb, "Definitions")
  
  ## Title Section
  wb_title <- "Allocation of Effort (CARTS) Definitions"
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 3, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 3, titleStyle, rows = 1, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 9
  
  
  ### Definitions Table 
  definitions <- data.frame(
  Category = c("Clinical", "Clinical With Resident", "Service", "Service With Resident",	"Non-Billable Offsite Clinical Time",
               "Department/ Hospital Admin",	"Residency Program Admin",	"Clinical Admin",	
               "Research",
               # "Research Funded",	"Research Unfunded", "Research Intramurally Funded",
               "School Teaching"),
  Definition   = c("Activities related to billable physician patient care. Any clinical services rendered and billed through the Faculty Practice.",
                   "Activities related to billable patient care with a resident present.",
                   "Clinical services rendered in Hospital locations for time spent in non-billable direct patient care activities such as Medicaid clinic visits where the professional fees are NOT billed or paid very poorly for services provided.",
                   "Clinical services rendered in Hospital locations for time spent in non-billable direct patient care activities such as Medicaid clinic visits where the professional fees are NOT billed or paid very poorly for services provided.",
                   "Activities related to non-billable physician patient care. None of the billing or RVUs roll back to Mount Sinai.",
                   "Work-effort related to administration of departmental services and programs; school-related administrative services. Work-effort related to administration of hospital related services. Administrative time associated with hospital services (critical care, stroke, etc.) should be defined as Hospital Administrative effort.",
                   "Any administrative time (with or without an official title) spent supporting the residency program. Administrative time associated with hospital clinic is considered Residency Program Administration time.",
                   "Clinical non-patient facing activities such as patient charting and patient communications.",
                   "Time spent executing grant related activities, including effort devoted to; extramurally sponsored research projects; research and/or clinical trial effort which is paid for by an institution budget or philanthropy account; to a sponsored research training program; effort devoted to sponsored clinical trials.",
                   "Preparation and instruction time related to teaching medical student courses and residency program effort (e.g., Grand Rounds). Time spent with residents performing clinical duties should be classified under clinical or service as appropriate."),
  Example = c("Time spent in the FPA without a resident present.",
              "Time spent in the FPA with a resident present.",
              "Ryan, IMA, inpatient clinics without a resident present.",
              "Ryan, IMA, inpatient clinics with a resident present.",
              "Time spent at EHC/QHC, Bronx VA, etc.",
              "Committee service, FPA quality roles, FPA Medical Director, IRB service, and other departmental services. Hospital-based Quality roles, Medical Directors of labs, clinics, operating rooms, inpatient units, or other hospital-based settings; Medical/Quality Directors (infection control).",
              "Residency Program Director, Fellowship Program Director (if accredited fellowship program), time spent on Grand Rounds presentations, interviews, resident evaluations, etc. should be included in this time.",
              "Time spent on charting, EPIC In-Basket Communications, etc.",
              "Sponsored/not sponsored research training, clinical trials, grant-funded activities.",
              " ")
)
  
  ### Data Output 
  writeDataTable(wb, 3, definitions, startRow = 3, startCol = 1, tableStyle = "TableStyleLight9")
  
  addStyle(wb, 3, createStyle(wrapText = TRUE),
           rows = (row_start):(row_start+nrow(definitions)),
           cols = c(1,2,3), gridExpand = TRUE)
  
  setColWidths(wb, 3, cols = c(1), widths = 35)
  setColWidths(wb, 3, cols = c(2), widths = 60)
  setColWidths(wb, 3, cols = c(3), widths = 40)
  
  
  # CPSC BENCHMARK Tab --------------------------------------------------------------
  addWorksheet(wb, "CPSC Benchmark")
  
  ## Title Section
  wb_title <- "CPSC Benchmark"
  titleStyle <- createStyle(fontSize = 16,
                            textDecoration = c("bold", "italic"), 
                            valign = "center")
  
  writeData(wb, 4, wb_title, startRow = 1, startCol = 1)
  addStyle(wb, 4, titleStyle, rows = 1, cols = 1)
  
  
  ### Set Default Column and Row Index
  
  month_col_num <- length(month_col_names)
  year_col_num <- length(year_col_names)
  
  row_start <- 3
  col_start <- 9
  
  
  ### CPSC Benchmark
  cpsc_benchmark <- cpsc_benchmark_tbl %>% 
    collect() %>%
    filter(YEAR_KEY >= 2023) %>%
    arrange(YEAR_KEY, SPECIALTY_DESCRIPTION_ORG)
    
  
  ### Data Output 
  writeDataTable(wb, 4, cpsc_benchmark, startRow = 3, startCol = 1, tableStyle = "TableStyleLight9")
  
  addStyle(wb, 4, number_format,
         rows = (row_start+1):(row_start+nrow(cpsc_benchmark)),
         cols = 5:length(cpsc_benchmark), gridExpand = TRUE)



  
  # Export Excel Report
  saveWorkbook(wb, paste0("~/monthly-productivity-file-email/department-files/Master Physician Productivity Data_",department_filter,"_",
                          month_col_names[length(month_col_names)],".xlsx"), overwrite = T)
  # saveWorkbook(wb, paste0("/nfs/data/Applications/Ambulatory/master_productivity_data_dept.xlsx"), overwrite = T)
  
  # openXL(wb)

}

```


```{r Department Excel Export Physicians, echo = FALSE, warning = FALSE, message = FALSE}

for (i in list_master_dept) {
  productivity_file_function(i)
}

```












